---
title: "Family Photo Archive (FPA) Apps"
author: "Rob Donald"
subtitle: "Research Running Log"
date: "`r format(Sys.time(), '%A %d %B %Y')`"
header-includes:
- \usepackage{graphicx}
output:
  pdf_document:
    fig_caption: yes
    toc: yes
    toc_depth: '2'
urlcolor: blue
---
\def\shrug{\texttt{\raisebox{0.75em}{\char`\_}\char`\\\char`\_\kern-0.5ex(\kern-0.25ex\raisebox{0.25ex}
{\rotatebox{45}{\raisebox{-.75ex}"\kern-1.5ex\rotatebox{-90})}}\kern-0.5ex)\kern-0.5ex\char`\_/\raisebox{0.75em}
{\char`\_}}}

```{r setup, include=FALSE}
# The above LaTex
# From https://tex.stackexchange.com/questions/279100/typeset-the-shrug-%C2%AF-%E3%83%84-%C2%AF-emoji (post by Mark Wibrow)
# The fig.pos = 'h' tells LaTeX to put the figure where you ask for it
knitr::opts_chunk$set(echo = TRUE,fig.height=8,fig.width=12,fig.pos = 'h')
options(width=80)
```

```{r library_setup, include=FALSE}
suppressMessages({suppressWarnings({
    library(dplyr)
    library(readr)
    library(lubridate)
    library(here)
    
    library(ggplot2)
    library(RobsRUtils)
    library(pander)
    library(kableExtra)

})})
```

# Abstract

A set of notes documenting the application(s) coded up to support the "Family Photo Archive" (FPA) project.

# 2021-11-21

## Initial Test Code

Reminding myself of and checking Python techniques for writing a support application to provide a base
archive backup of the meta data from the macOS Photos App database.

This is a python 3.x project using VS code with the documentation coded up with RStudio and Rmarkdown to .pdf.

##  Python Module osxphotos

Came across this module which appears to provide *exactly* what I need.

* (https://github.com/RhetTbull/osxphotos)



## Building Strings For .csv

Looking at the ways of extracting info from the xxx object and building a string 
for output to a .csv

From memory the method is build a CSV string for the header, extract the bits row by row then
"joining" it with a delimiter (e.g. string_for_csv = sb.join(',') or something like this \small\shrug\normalsize).

I then came across this article which looks promising.

See (https://levelup.gitconnected.com/building-csv-strings-in-python-32934aed5a9e)








